Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-14 README.Rmd
added a clarification
changes to fix font size issue in Figure 11 and cut off text in Figure 12

- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the paper. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the paper.
- `raw` contains the raw versions of the data files that the above datasets are derived from.

@@

The font sizes in the figures are calculated based on how the figures are scaled due to the specification of both fig.width and out.width in the Rnw file to ensure that they are consistent across figures. The text sizes are either set to 7 pt or 5.5 pt as indicated by the table below. Note that the text in the paper is 9 pt and a similar approach was used to ensure that line sizes are larger than 0.5 pt.

@@

>>>>

- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the paper. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the paper.
- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from.

@@

The font sizes in the figures are calculated based on how the figures are scaled due to the specification of both fig.width and out.width in the Rnw file to ensure that they are consistent across figures. The text sizes are either set to 7 pt or 5.5 pt (Helvetica) as indicated by the table below. Note that the text in the paper is 9 pt (Times) and a similar approach was used to ensure that line sizes are larger than 0.5 pt.

@@

Note: The only figure that does not follow these values is Figure 11 where the facet labels were set to font size 5 (Helvetica) in order for them to fit appropriately.

### 2020-09-14 paper.Rnw
changes to fix font size issue in Figure 11 and cut off text in Figure 12

# Create a feature heatmap
plot_feature_heatmap(
  bullet_explain %>%
    mutate(
      label = as.factor(label),
      feature = fct_recode(
        feature,
        "Rough Correlation" = "rough_cor",
        "Consecutively Matching Striae" = "cms",
        "Distance" = "D",
        "Matches" = "matches",
        "Mismatches" = "mismatches",
        "Non-Consecutively Matching Striae" = "non_cms",
        "Cross Correlation Function" = "ccf",
        "Sum of Peaks" = "sum_peaks",
        "Distance Standard Deviation" = "sd_D"
      )
    ),
  facet_var = bullet_test %>%
    mutate(samesource = fct_recode(
      factor(samesource),
      "Match" = "TRUE",
      "Non-Match" = "FALSE"
    )) %>%
    pull(samesource) %>%
    na.omit(),
  order_method = "PCA"
) +
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  scale_color_gretchenalbrecht(palette = "last_rays",
                               discrete = TRUE,
                               reverse = TRUE) +
  theme_bw(base_family = ff, base_size = f11_fs) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    strip.background = element_rect(color = "white", fill = "white"),
    strip.text.y.right = element_text(angle = 0),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  guides(fill = guide_legend(nrow = 3)) +
  labs(y = "Case", color = "Complex Model Feature", fill = "Complex Model Feature")

>>>>

# Create a feature heatmap
plot_feature_heatmap(
  bullet_explain %>%
    mutate(
      label = as.factor(label),
      feature = fct_recode(
        feature,
        "Rough Correlation" = "rough_cor",
        "Consecutively Matching Striae" = "cms",
        "Distance" = "D",
        "Matches" = "matches",
        "Mismatches" = "mismatches",
        "Non-Consecutively Matching Striae" = "non_cms",
        "Cross Correlation Function" = "ccf",
        "Sum of Peaks" = "sum_peaks",
        "Distance Standard Deviation" = "sd_D"
      )
    ),
  facet_var = bullet_test %>%
    mutate(samesource = fct_recode(
      factor(samesource),
      "Match" = "TRUE",
      "Non-Match" = "FALSE"
    )) %>%
    pull(samesource) %>%
    na.omit(),
  order_method = "PCA"
) +
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  scale_color_gretchenalbrecht(palette = "last_rays",
                               discrete = TRUE,
                               reverse = TRUE) +
  theme_bw(base_family = ff, base_size = f11_fs) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    strip.background = element_rect(color = "white", fill = "white"),
    strip.text.y.right = element_text(angle = 0, size = f11_fs*0.7),
    strip.text.x = element_text(size = f11_fs*0.7),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  guides(fill = guide_legend(nrow = 3)) +
  labs(y = "Case", color = "Complex Model Feature", fill = "Complex Model Feature")
